### 2017-03-28 Manuscripts/cog-psych/cogpsych.tex
edits to e2 results, added figures

@@

122 participants were recruited from Amazon Mechanical Turk. 61 participants were randomly assigned to the Middle and Bottom conditions each. The stimuli were exactly as in Experiment 1. Again, the assignment of perceptual features (color, size) to axes of the domain space (x, y) was counterbalanced across participants.

The procedure was exactly as in Experiment 1: participants first completed a short training phase, followed by the generation phase, followed by the generalization phase (data from this phase is not discussed in this report).

@@

Because the conditions differ only in the Y-axis position of the experimenter-defined category, we began by comparing the conditions in terms of the frequency with which participants generated examples above and below the categories: we counted the number of participants in each condition who placed at least one `Beta' exemplar on the top and bottom `rows' of the space (the maximum and minimum possible y-axis value, respectively). The resulting contingencies data are shown in Table \ref{table:e2-subset-table}. Fisher's Exact Tests reveal that more Middle participants generated an exemplar in the bottom row , $p < 0.001$, but the conditions did not differ in use of the top of the space, $p = 0.16$. More Middle participants placed exemplars in the top \textit{and} bottom rows, $p = 0.038$.

@@

>>>>

This constraint, however, only serves to signify one possible account of category generation: the nature of PACKER's account can be drastically altered through changes to the $\phi$ and $\gamma$ parameters. Furthermore, by fitting these parameters to a dataset, one can describe the relative roles of between-class contrast and within-class similarity in generation. For example, as will be discussed in more detail below, PACKER is formally equivalent to the copy-and-tweak model proposed by \cite{jern2013probabilistic} when $\phi = 0$ and $\gamma = 1$. Likewise, when $\phi < 0$ and $\gamma = 0$, PACKER represents a contrast-only generation mode, relying exclusively on contrast when generating new categories. Finally, when $\phi = \gamma < 0$, PACKER represents a ``pure-packing'' approach, placing exemplars in any unoccupied area of the domain. Thus, beyond specifying PACKER's core proposal, the $\phi$ and $\gamma$ allow the us to address a wide variety of qualitatively distinct generation strategies.

@@

\subsection{Participants, Materials, \& Procedure}

122 participants were recruited from Amazon Mechanical Turk. 61 participants were randomly assigned to the Middle and Bottom conditions each. The stimuli were exactly as in Experiment 1. Again, the assignment of perceptual features (color, size) to axes of the domain space (x, y) was counterbalanced across participants. The procedure was exactly as in Experiment 1: participants first completed a short training phase, followed by the generation phase, followed by the generalization phase (data from this phase is not discussed in this report).

@@

\begin{figure}
    \begin{center}
    \inputpgf{figs/}{e2-samples.pgf}
    \caption{Sample categories generated in Experiment 2. }
    \label{fig:e2-samples}
    \end{center}
\end{figure}

As in Experiment 1, we observed broad differences in the generation approach taken by different participants.  To characterize the nature of these differences, Figure \ref{fig:e2-samples} depicts sample categories generated by participants. The data from each condition in Figure \ref{fig:e2-samples} is organized into four columns based on commonly observed patterns of generation: a `Cluster' type of tightly-clustered examples,   `Row' and `Column' types of exemplars widely distributed along the one axis but narrowly along the other, and a `Corners' type, wherein participants placed exemplars in disparate corners of the space. As before, in this section we focus no what can be concluded from analyzing the data in aggregate, but in a later section we will focus more specifically on explaining the individual differences.

We began our analysis by again testing for the broad influence of category contrast on generation. As in Experiment 1, we computed the frequency each stimulus was generated as a function of its average distance from members of the experimenter defined category, as well as each participant's average within- and between- category distance. These data, shown in Figure \ref{fig:e2-distanceplots}, yield highly similar results. Stimuli that are more distant from members of the experimenter=-defined category were more frequently generated, and the categories in each condition tended to possess more between-class than within-class distance: Bottom, $t(60) = 5.5$, $p < 0.001$; Middle, $t(60) = 2.71$, $p = 0.009$.

We did, however, observe a notable subgroup of participants in each condition who generated categories with more within-class than between-class distance. Upon manual inspection, many of these individuals appear to have assumed a `Corners' strategy, placing exemplars in disparate corners of the space, thus producing much more within-class distance, see Figure \ref{fig:e2-samples} for examples.

\begin{figure}
    \begin{center}
    \inputpgf{figs/}{e2-distanceplots.pgf}
    \caption{Experiment 2 results. \textit{Left}: Frequency of generation as a function of distance from members of the experimenter-defined category. \textit{Right}: Scatter plot of within-class versus between-class distance in each of the participant-generated categories.}
    \label{fig:e2-distanceplots}
    \end{center}
\end{figure}

Because the conditions differ only in the Y-axis position of the experimenter-defined category, we then compared the conditions in terms of the frequency with which participants generated examples above and below the categories. Specifically, we counted the number of participants in each condition who placed at least one `Beta' exemplar on the top and bottom `rows' of the space (the maximum and minimum possible y-axis value, respectively). The resulting contingencies data are shown in Table \ref{table:e2-subset-table}. Fisher's Exact Tests reveal that more Middle participants generated an exemplar in the bottom row , $p < 0.001$, but the conditions did not differ in use of the top of the space, $p = 0.16$. More Middle participants placed exemplars in the top \textit{and} bottom rows, $p = 0.038$.

@@

\section{Simulations}

\section{General Discussion}
